Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering

### 2016-07-11 paper/structureScene.tex
first pass on sections 5 and 6

Different sets of parameters were tested to compute the MFFCs. We here report only the results for the best setting, which is similar to the one used by the winners of the previous DCASE 2013 challenge \cite{roma2013}. 40 MFCCs (including the first energy coefficient) are computed for windows of 50ms and hops of 25ms, with a limited frequency range going from $27.5$Hz to $1000$Hz. This setting gives us 600 feature vectors per scenes. It has been reported that classifying the full set of frames directly may not be the best approach \cite{rakotomamonjy2015histogram}. In order to reduce the data dimensionality, a pooling step is performed on the MFCCs vectors: each set of MFCCs vectors is dividing into $n$ non-overlapping $t$-seconds long slices. Each $n$ MFCC slices is then averaged over time. As the \emph{ob} approaches involve a clustering step, it is desirable to ensure that each scene is described by circa the same number of vectors prior to running the clustering, for both the temporal-scattering and the MFCCs. Thus, $t$ is set to 250ms, which gives us 120 MFCCs vectors per scenes.

\subsection{Acoustic Scene Similarity and Classification}

The influence of the temporal-scattering transform and the \emph{ob} approaches are assessed in an unsupervised setting (\emph{i.e.} ASS) and in a supervised setting (\emph{i.e.} ASC).

For the ASS setting, evaluation is performed on the private dataset of the DCASE 2013 challenge. The metric used is the precision at rank $k$ ($p@k$), which is the  average  number  of  items  of  the  same  class among the $k$ closest items averaged for all possible seed items. The $p@k$ is computed for $k=[1,\ldots,9]$. Note that a $p@1$ is equivalent to an accuracy computed based on the labels of the 1st nearest neighbors of the items to classify. For each experimental setting, we only report the results obtained with the sets of parameters, \emph{i.e.} the number of clusters $m$ for the \emph{ob} approaches and the scaling parameter $N$ of the RBF kernels (see Eq. \ref{eq:kc}) leading to the best $p@9$.

@@

The \emph{ob} approaches are compared to commonly used approaches using an early integration strategy (\emph{ei}) for the ASS setting, and both an early and a late integration (\emph{li}) strategy for the ASC setting (see Section \ref{sec:eili}).

\subsection{Classifier}

@@

For the \emph{ob} approaches, we use the precomputed kernels described in Section \ref{sec:object}. For both the \emph{ei} and \emph{li} approaches, a linear kernel as well as a RBF kernel are used. As for the \emph{ob} approaches, the RBF kernel is scaled locally using the method proposed in \cite{selfTuneManor2004}. All feature vectors, being frames, pooled frames or centroids, depending on the approach considered, are standardized prior to be filled into the classifier. The standardization is computed with respect to the train/test set splits of the cross validation scheme (see Section \ref{sec:stand}).

\section{Results: Acoustic Scene Similarity}

@@

\section{Results: Acoustic Scene Classification}

>>>>

Different sets of parameters were tested to compute the MFCCs. Results here are only reported for the best setting, which is similar to the one used by the winners of the previous DCASE 2013 challenge \cite{roma2013}. 40 MFCCs (including the first energy coefficient) are computed for windows of 50ms and hops of 25ms, with a limited frequency range going from $27.5$Hz to $1000$Hz. This setting gives us 600 feature vectors per scenes. It has been reported that classifying the full set of frames directly may not be the best approach \cite{rakotomamonjy2015histogram}. In order to reduce the data dimensionality, a pooling step is performed on the MFCCs vectors: each set of MFCCs vectors is divided into $n$ non-overlapping $t$-seconds long "texture" windows. Each $n$ texture windows are then averaged over time. As the \emph{ob} approaches involve a clustering step, it is desirable to ensure that each scene is described by circa the same number of vectors prior to the clustering step, for both the temporal-scattering and the MFCCs. Thus, $t$ is set to 250ms, resulting in 120 MFCCs texture windows per scene.

\subsection{Methods}

The influence of the temporal-scattering transform and the \emph{ob} approaches are assessed in an unsupervised setting (\emph{i.e.} ASSR) and in a supervised setting (\emph{i.e.} ASC).

For the ASSR setting, evaluation is performed on the private dataset of the DCASE 2013 challenge. The metric used is the precision at rank $k$ ($p@k$), which is the  average  number  of  items  of  the  same  class among the $k$ closest items averaged for all possible seed items. The $p@k$ is computed for $k=[1,\ldots,9]$, $9$ being the number of elements that are of the same class than the seed item. Note that a $p@1$ is equivalent to an accuracy computed based on the labels of the 1st nearest neighbors of the items to classify. For each experimental setting, we only report the results obtained with the sets of parameters, \emph{i.e.} the number of clusters $m$ for the \emph{ob} approaches and the scaling parameter $N$ of the RBF kernels (see Eq. \ref{eq:kc}) leading to the best $p@9$.

@@

The \emph{ob} approaches are compared to commonly used approaches using an early integration strategy (\emph{ei}) for the ASSR setting, and both an early and a late integration (\emph{li}) strategy for the ASC setting (see Section \ref{sec:eili}). In thsi context early integration refers to an averaging of the features and late integration refers to a majority voting of the predictions.

@@

For the \emph{ob} approaches, we use the precomputed kernels described in Section \ref{sec:object}. For both the \emph{ei} and \emph{li} approaches, a linear kernel as well as a RBF kernel are used. As for the \emph{ob} approaches, the RBF kernel is scaled locally using the method proposed in \cite{selfTuneManor2004}. All feature vectors, being frames, texture windows or centroids are standardized prior to be given to the classifier. The standardization is computed with respect to the train/test set splits of the cross validation scheme (see Section \ref{sec:stand}).

\section{Acoustic Scene Similarity Retrieval}

@@

\section{Acoustic Scene Classification}
